How to use flowCore package

### 2006-11-26 inst/doc/HowTo-flowCore.Rnw
rename fcsFrame/Set to flowFrame/Set
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@21270 bc3139a8-67e5-0310-9ffc-ced21a209358

\usepackage{times}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{times}
\usepackage{comment}
\usepackage{subfigure}

@@

\newlength{\smallfigwidth}
\setlength{\smallfigwidth}{6cm}

@@

<<showB08,echo=TRUE>>=
show(b08)
@

We can plot the raw data for the FSC-H and SSC-H parameters.
<<plotRaw1,eval=TRUE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(1,2))
@
<<plotRaw2,eval=FALSE,echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(3,4))
@ 
\begin{verbatim}
> basicplot(b08,plotParameters=c(1,2))
> basicplot(b08,plotParameters=c(3,4))
> basicplot(e07,plotParameters=c(1,2))
> basicplot(f06,plotParameters=c(1,2))
\end{verbatim}

@@

A log transformation is of type: parameter=log(parameter,logbase) * r/d
<<logTransform,echo=FALSE,results=hide>>=
logTransform <- new("logTransformation",transformationId="Log-Transformation",
                parameters="FSC-H", r=1, d=1,logbase=2)
data08LogTransform <- applyTransformation(logTransform,b08)
@ 
\begin{verbatim}
>logTransform <- new("logTransformation",transformationId="Log-Transformation",
+                parameters="FSC-H", r=1, d=1,logbase=2)
>data08LogTransform <- applyTransformation(logTransform,b08)
\end{verbatim}

<<ResultTransfoLinear>>=
b08@exprs[1:5]
#Linear transformation
data08Transform@exprs[1:5]
##Log base 2 transformation
data08LogTransform@exprs[1:5]
@

@@

<<define and apply rectangleGate1,eval=TRUE, echo=FALSE,results=hide>>=
min1 <- 200
max1 <- Inf
fil1 <- new("rectangleGate",filterId="nonDebris",
            parameters="FSC-H",min=min1,max=max1)
b08fil1 <- applyFilter(fil1,b08)
@ 
<<plotfiltered, eval=FALSE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08fil1,pch="*")
@ 
<<define and apply polygonGate2,eval=TRUE, echo=FALSE,results=hide>>=
min2 <- 200
max2 <- 500
centerFilter <- new("rectangleGate",filterId="center",
            parameters=c("FSC-H"), min=min2, max=max2)
b08centerFilter <- applyFilter(centerFilter,b08)
@ 
<<plotCenterfiltered, eval=FALSE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08centerFilter,pch="*")
@

%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{plotfiltered} A}
%%\subfigure{\includegraphics[width=40mm]{plotCenterfiltered} B} 
%%\caption{
%%  \label{fig:Fig02}{Example of the effect of filtering with a
    rectangular gate.}} 
%%\end{figure}

@@

<<plotRectanglefilter, eval=FALSE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08sqrfilter,pch="*")
@

@@

<<plotTrianglefilter, eval=FALSE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(x=b08,y=b08Trgfilter,filter=trianglefilter,colSubSet="red",pch="*")
@

%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{plotRectanglefilter} A}
%%\subfigure{\includegraphics[width=40mm]{plotTrianglefilter} B} 
%%\caption{
%%  \label{fig:Fig03}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<SelectNonDebris,eval=TRUE,echo=FALSE,results=hide>>=
min1 <- c(200,0)
max1 <- c(800,800)
filter1 <- new("rectangleGate",filterId="Nondebris",parameters=c("FSC-H","SSC-H"),
  min=min1,max=max1)

@@

tab <- c("B08"=sum(b08.result1@subSet),"E07"=sum(e07.result1@subSet),"F06"=sum(f06.result1@subSet))
@

<<plotResFilter1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result1,main="B08",pch="*")
@ 
<<plotResFilter2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(e07,y=e07.result1,main="E07",pch="*")
@ 
<<plotResFilter3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,y=f06.result1,main="F06",pch="*")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{plotResFilter1}}
%%\subfigure{\includegraphics[width=40mm]{plotResFilter2}} 
%%\subfigure{\includegraphics[width=40mm]{plotResFilter3}} 
%%\caption{
%%  \label{fig:Fig05}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<FL1Filtered1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result3,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered2, echo=FALSE, eval=FALSE,fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result4,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered3, echo=FALSE, eval=FALSE,fig=TRUE, prefix=FALSE, include=FALSE>>=
basicplot(b08,y=b08.result5,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@

>>>>

\usepackage{times}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{times}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{subfigure}

@@

@@

<<showB08,eval=FALSE,echo=FALSE>>=
show(b08)
@

We can plot the raw data for the FSC-H and SSC-H parameters.
<<plotRaw1,eval=TRUE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(1,2))
@
<<plotRaw2,eval=TRUE,echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(b08,plotParameters=c(3,4))
@ 
\begin{verbatim}
> plot(b08,plotParameters=c(1,2))
> plot(b08,plotParameters=c(3,4))
> plot(e07,plotParameters=c(1,2))
> plot(f06,plotParameters=c(1,2))
\end{verbatim}

@@

A log transformation is of type: parameter=log(parameter,logbase) * r/d
<<logTransform,echo=FALSE,results=hide>>=
logTransform <- new("logTransformation",transformationId="Log-Transformation",
                parameters="FSC-H", r=1, d=1,logbase=2)
data08LogTransform <- applyTransformation(logTransform,b08)
@ 
\begin{verbatim}
>logTransform <- new("logTransformation",transformationId="Log-Transformation",
+                parameters="FSC-H", r=1, d=1,logbase=2)
>data08LogTransform <- applyTransformation(logTransform,b08)
\end{verbatim}
<<ResultTransfoLinear>>=
b08@exprs[1:5]
#Linear transformation
data08Transform@exprs[1:5]
##Log base 2 transformation
data08LogTransform@exprs[1:5]
@

@@

<<define and apply rectangleGate1,eval=TRUE, echo=FALSE,results=hide>>=
min1 <- 200
max1 <- Inf
fil1 <- new("rectangleGate",filterId="nonDebris",
            parameters="FSC-H",min=min1,max=max1)
b08fil1 <- applyFilter(fil1,b08)
@ 
<<plotfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08fil1,pch="*")
@ 
<<define and apply polygonGate2,eval=TRUE, echo=FALSE,results=hide>>=
min2 <- 200
max2 <- 500
centerFilter <- new("rectangleGate",filterId="center",
            parameters=c("FSC-H"), min=min2, max=max2)
b08centerFilter <- applyFilter(centerFilter,b08)
@ 
<<plotCenterfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08centerFilter,pch="*")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotfiltered} A}
\subfigure{\includegraphics[width=40mm]{plotCenterfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering with a rectangular gate.}} 
\end{figure}

@@

<<plotRectanglefilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08sqrfilter,pch="*")
@

@@

<<plotTrianglefilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(x=b08,y=b08Trgfilter,filter=trianglefilter,colSubSet="red",pch="*")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotRectanglefilter} A}
\subfigure{\includegraphics[width=40mm]{plotTrianglefilter} B} 
\caption{
  \label{fig:Fig03}{Example of the effect of filtering with a
    polygon gate.}} 
\end{figure}

@@

<<SelectNonDebris,eval=TRUE,echo=FALSE,results=hide>>=
min1 <- c(200,0)
max1 <- c(800,800)
ilter1 <- new("rectangleGate",filterId="Nondebris",parameters=c("FSC-H","SSC-H"),
  min=min1,max=max1)

@@

tab <- c("B08"=sum(b08.result1@subSet),"E07"=sum(e07.result1@subSet),"F06"=sum(f06.result1@subSet))
@ 
<<plotResFilter1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result1,main="B08",pch="*")
@ 
<<plotResFilter2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(e07,y=e07.result1,main="E07",pch="*")
@ 
<<plotResFilter3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(f06,y=f06.result1,main="F06",pch="*")
@ 
%%\begin{figure}
%%\centering
%%\subfigure{\includegraphics[width=40mm]{plotResFilter1}}
%%\subfigure{\includegraphics[width=40mm]{plotResFilter2}} 
%%\subfigure{\includegraphics[width=40mm]{plotResFilter3}} 
%%\caption{
%%  \label{fig:Fig05}{Example of the effect of filtering with a
%%    polygon gate.}} 
%%\end{figure}

@@

<<FL1Filtered1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result3,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered2, echo=FALSE, eval=FALSE,fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result4,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered3, echo=FALSE, eval=FALSE,fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result5,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@
